Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-09 doc/paper.Rmd
some additions on coarseness discussion

\hh{In the next page and a half it is easy to lose the red line. It might help to include a table with an overview.
The table should include the reference to the paper, the data used, the statistical method and the associated error rates.}
\gk{table included}
Various toolmarks have been studied in the literature:  \citet{manytoolmarks1} and \citet{chumbley} have been analyzing screwdriver marks  digitized using a profilometer;  \citet{manytoolmarks2} have investigated 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope; \citet{afte-chumbley} have been investigated digitized marks from slip-joint pliers generated by a surface profilometer.

\hh{We need an additional sentence here to get from the data to the statistical methods ... }
\gk{Analysis of these digitized markings require the use of statistical methods which can quantify the scientific mechanism of comparing markings and serve as metrics for correctly identifying the error rate.}
\citet{manytoolmarks2} define a relative distance metric and use it as similarity measure between two toolmarks. \citet{manytoolmarks1} extract many small segments in the markings of two toolmarks and compare similiarity using a maximum pearson correlation coefficient. 
The Chumbley scoring method, first introduced by \citet{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  \citep{hadler} make the score deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segements of striae.  In this paper, we are investigating the applicability of the Chumbley scoring method by \citet{hadler} to assess striation marks on bullet lands for same-source identification.

@@

roc.summary <- cvcs %>% group_by(wo, wv, method) %>%
  summarize(
    eer = EER(1-p_value, match),
    auc = AUC(1-p_value, match)
  )
p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Equal Error rate (EER)") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = c(0.25, 0.25))

p2 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=auc, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Area under the curve (AUC)") +
  xlab("Size of optimization window in pixels")+
  theme(legend.position = c(0.75, 0.25))
grid.arrange(p1, p2, nrow=1)
```

>>>>

\hh{In the next page and a half it is easy to lose the red line. It might help to include a table with an overview.
The table should include the reference to the paper, the data used, the statistical method and the associated error rates.}
Various toolmarks have been studied in the literature:  \citet{manytoolmarks1} and \citet{chumbley} have been analyzing screwdriver marks  digitized using a profilometer;  \citet{manytoolmarks2} have investigated 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope; \citet{afte-chumbley} have been investigated digitized marks from slip-joint pliers generated by a surface profilometer.

\hh{We need an additional sentence here to get from the data to the statistical methods ... }
\citet{manytoolmarks2} define a relative distance metric and use it as similarity measure between two toolmarks. \citet{manytoolmarks1} extract many small segments in the markings of two toolmarks and compare similiarity using a maximum pearson correlation coefficient. 
The Chumbley scoring method, first introduced by \citet{chumbley}, uses a similar but more extensive framework based on a Mann-Whitney U test of the resulting correlation coefficients. This approach is non-deterministic, because segments are chosen randomly.  \citep{hadler} make the score deterministic for each pair of toolmarks by choosing segments for comparison systematically. This approach also ensures independence between segements of striae.  In this paper, we are investigating the applicability of the Chumbley scoring method by \citet{hadler} to assess striation marks on bullet lands for same-source identification.

@@

roc.summary <- cvcs %>% group_by(wo, wv, method) %>%
  summarize(
    eer = EER(1-p_value, match),
    auc = AUC(1-p_value, match)
  )
p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Equal Error rate (EER)") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = c(0.3, 0.2))

p2 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=auc, shape=factor(wv))) +
  geom_point() +
  facet_wrap(~method, labeller="label_both") + 
  theme_bw() +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Area under the curve (AUC)") +
  xlab("Size of optimization window in pixels")+
  theme(legend.position = c(0.7, 0.2))
grid.arrange(p1, p2, nrow=1)
```
